
% Select 'print' for paper-printing version
\documentclass[print]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Disable hyphenation
\usepackage[none]{hyphenat}

% For GitHub and LinkedIn
\usepackage{fontawesome}
\usepackage[hidelinks,baseurl=https://]{hyperref}

\name{Yang Deng}
\address{\mbox{\faGithub\quad\url{github.com/dyrobin}} \linebreak \mbox{\faLinkedin\quad\url{linkedin.com/in/dyrobin}}}
\contacts{+358 (0) 50 4424616 \linebreak \url{yang.r.deng@gmail.com}}

\begin{document}
	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Profile}
		\begin{cvsubsection}{}{}{}	
		I am a dedicated and quality-minded software engineer with many years experience in product development using modern technologies. I have a clear logical mind to take a practical approach to problem-solving and a strong willingness to make the solutions come into effect. I am never afraid of new things and often my solid programming knowledge will help me learn them faster. Also, I am an enthusiast of agile development and I believe fast iteration is the core competence of the team and the product it develops. Currently I am looking for an opportunity to utilize my skills in a challenging working environment and become a valuable asset to the organisation that I work for.
		\end{cvsubsection}	
	\end{cvsection}
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Senior Software Engineer}{Helvar}{May 2017 -- Present}
			Lighting Intelligence Platform
			\begin{itemize}
			    \item Designed and implemented (Node.js) components of cloud gateway for ActiveAhead wireless lighting system where each component runs as a microservice and RabbitMQ is used as message broker and Redis as database. The gateway uses AWS IoT not only for communication but also for other tasks like gateway provisioning/registration, certificate management, software update, access control, etc.
				\item Created scripts (Makefile, Bash, Python) to build, configure, deploy and run cloud gateway using Docker image/container
				\item Developed parts of cloud backend using AWS Lambda, co-designed schema of AWS DynamoDB (NoSQL) and AWS RDS (SQL) tables, formed feature stack where other AWS services are used, for example S3, Kinesis, ElasticSerarch, API Gateway, Elastic Container Registry, CloudWatch, IAM, etc
				\item Authored two internal libraries (rabbitmq-client and logger) and published them into company's NPM registry (both have 100\% test coverage and are widely used within the team)
				\item Built integration and end-to-end testing frameworks using PyTest (Python) and collaborated with Devops in Jenkins integration
				\item Contributed definition of development procedure where coding style, code quality check (SonarQube), unit test coverage, CI/CD, Git flow, release process are involved
				\item Worked with both Scrum and Kanban, acted as scrum master for more than 1 year
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Engineer}{LUMO Connections}{Nov. 2016 -- Apr. 2017}	
			Smart Lamp
			\begin{itemize}
				\item Implemented RESTful APIs by Express framework (Node.js) on Raspberry Pi
				\item Developed a tiny HTTP server (C/C++) that integrated with WiFi manager on ESP8266 (NodeMCU)
			\end{itemize}
		\end{cvsubsection}
			
		\begin{cvsubsection}{Software Engineer, Researcher}{Aalto University}{Sept. 2011 -- Oct. 2016}	
			Adaptive 6LoWPAN Packet Size Control
			\begin{itemize}
				\item Applied SciPy to analyse and visualize massive 6LoWPAN packet data
				\item Proposed \textit{first linear then exponential} algorithm that improved throughput up to 40\%
				\item Presented paper in a well-known conference EWSN2015
			\end{itemize}
			\smallskip
			Multicast for Constrained Networks
			\begin{itemize}
				\item Implemented a prototype of IPv6 Multicast Listener Discovery on Contiki OS
				\item Established a test bed for MPL (RFC7731) and evaluated its performance against flooding 
				\item Drafted a simplified multicast protocol for constrained networks based on PIM-SSM
			\end{itemize}
			\smallskip
			MAMMOTH - Massive Scale Machine to Machine Service
			\begin{itemize}
				\item Implemented an HTTP-CoAP mapping layer on Contiki OS
				\item Deployed more than 1000 emulated and real constrained devices on the platform
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Software Engineer}{Nokia Research Center}{Nov. 2009 -- Aug. 2011}	
			Rich Context Mobile Platform
			\begin{itemize}
				\item Developed a publish-subscribe messaging mechanism for widgets on N900
				\item Filed a patent (US 20140237486 A1) on inter-widget communication
			\end{itemize}
			\smallskip
			Handwriting Calculator
			\begin{itemize}
				\item Implemented user interface using GTK+ on Maemo platform
				\item Released on Nokia Beta Labs and won outstanding project award
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Engineer, Intern}{IBM}{June 2009 -- Sept. 2009}	
			\begin{itemize}
				\item Tested localization and globalization translations for Lotus Software
				\item Developed a Perl script to detect empty translations of the content
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Additional Project Experience}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Web Developer (2017): Developed a LAMP website to calculate sales commission for 3 tourist retails
				\item Web Developer (2016): Built an e-commerce website (\url{store.kanssani.fi}) using WooCommerce
				\item Website Administrator (2012 - 2016): Maintained a phpBB forum for scholar and student community
				\item Teaching Assistant (2015): Taught two course assignments (P2P networking and WiFi positioning)
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Espoo, Finland}{Aalto University}{Sept. 2011 -- Aug. 2016}
			\begin{itemize}
				\item Ph.D candidate in Computer Science and Engineering. GPA: 4.77/5
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}[2]{Beijing, China}{Beijing University of Posts and Communications}{Sept. 2003 --  Apr. 2010}
			\begin{itemize}
				\item Master's Degree in Computer Networking, April 2010. GPA: 4.0/5				 
				\item Bachelor's Degree in Computer Science and Engineering, June 2007. GPA: 4.4/5
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Skills}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Programming: JavaScript(Node.js), Python, Bash, C/C++, Java
				\item Platform: Unix/Linux, AWS services, Docker
				\item Utilities: MySQL, NoSQL (Redis, DynamoDB, ElasticSearch), RabbitMQ
				\item Tools: Git, GNU Make, Jenkins, Sonarqube, Jira, VSCode
				\item Knowledge: Scrum, Kanban, Microservices, TDD/BDD, RESTful API, OOP, DevOps
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
\end{document}
